FraCaS: Temporal Analysis

### 2020-10-09 paper2020/paper.tex
clarify todos
address comparision with Androutsopoulos1998time

Unicity of action plays the role of event coreference in
(neo-)davidsonian account \todo{citation}. It is also a fine-grained
principle, allowing coreference to take into account certain arguments
when referencing. As we detail below, taking arguments into account
yields is critical to handle repeatability of achievements.

@@

\begin{equation}
  \label{eq:smith-novel-1}
\begin{array}{l}
∀x. novel(x) ∧ \\
∃t_1,t_2. [t_1,t_2] ⊆ 1991 ∧ write(smith,x,t_1,t_2) ∧ \\
∃t_3,t_4. [t_3,t_4] ⊆ 1992 ∧ write(smith,x,t_3,t_4) \\
⟶ ⊥ \\
\end{array}
\end{equation}
Note here that the scope for the existential is extended beyond the
scope of \textbf{P1}, and its polarity switched (to universal). This extension can work according to
\citet{unger_dynamic_2011}, and our implemented analysis of
anaphora\ifanon (citation anonymized)
\else\citep{bernardy_computational_2018,bernardy_wide-coverage_2019}\fi.

@@

>>>>

Unicity of action plays the role of event coreference in
(neo-)davidsonian account \todo{stergios: citation}. It is also a fine-grained
principle, allowing coreference to take into account certain arguments
when referencing. As we detail below, taking arguments into account
yields is critical to handle repeatability of achievements.

@@

\begin{equation}
  \label{eq:smith-novel-1}
\begin{array}{l}
∀x. novel(x) ∧ \\
∃t_1,t_2. [t_1,t_2] ⊆ 1991 ∧ write(smith,x,t_1,t_2) ∧ \\
∃t_3,t_4. [t_3,t_4] ⊆ 1992 ∧ write(smith,x,t_3,t_4) \\
⟶ ⊥ \\
\end{array}
\end{equation}
Note here that the scope for the existential is extended beyond the
scope of \textbf{P1}, and its polarity switched (to universal). This extension can follow the account of
\citet{unger_dynamic_2011}, and our implemented analysis of
anaphora\ifanon (citation anonymized)
\else\citep{bernardy_computational_2018,bernardy_wide-coverage_2019}\fi.

@@

Outside of inference, formal interpretation of tense is found in
natural-language interface to databases. Of note is the work of
\citet{androutsopoulos1998time}, which handles many of the time-aware
adverbial clauses that we address. However, we cover many more
interaction logical aspects of inference, such as coreference via
unity of action and interaction with quantifiers.
